### 2021-11-16 input/figsimplerproblem.tex
separating issues

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}(both) $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}(top) $c$ deletes its partition. (bottom)
    $a$ and $c$ delete their partition. (both) $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}(bottom) $b$ blocks the only transiting
      $\delta_a$ despite it propagated $\alpha_a$ before. (both) $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}(both) $b$ delivers and forwards $\delta_c$. (top)
    It reaches $a$ that answers with $\alpha_a$. $b$ delivers $\alpha_a$ again. (both) $c$
    stays in $P_a$.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages may be insufficient
    to guarantee consistent partitioning. In the bottom scenario, if
    $c$ had children, they would stay in the wrong partition
    too. Despite both scenarios look the same from $c$'s perspective,
    $c$ must acknowledge $P_a$'s \emph{possible} deletion and
    propagate it.}
\end{figure*}

>>>>

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $c$ delete their partition 
     while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ while $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}$b$ delivers and forwards $\delta_c$. $c$
    stays in the deleted partition $P_a$.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages may be insufficient
    to guarantee consistent partitioning. In the bottom scenario, if
    $c$ had children, they would stay in the wrong partition
    too.

    % Despite both scenarios look the same from $c$'s perspective, $c$
    % must acknowledge $P_a$'s \emph{possible} deletion and propagate
    % it.
  }
\end{figure*}

### 2021-11-16 input/proposal.tex
separating issues

At any time, a source can revoke its self-appointed status of source
by executing a \texttt{Del} operation, hence deleting its partition
from the system. All \processes that belong to this partition must
eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, \Process~$a$ deletes its partition. It notifies
all neighboring \processes~--~here only \Process~$b$~-- that may
belong to its partition using \NAMEB. Upon receipt, \Process~$b$
discards the \underline{d}elete notification $\delta_a$ since
$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
sends its own best partition $\alpha_d^3$ that may be the best for
\Process~$a$. Eventually, every \process belongs to Partition
$P_d$. In this scenario, they reach consistent partitioning.

@@

@@

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issues with
dynamic partitions even in simple scenarios comprising three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB} (bottom), both $a$ and $c$ delete their
partition while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC} (bottom), $b$ receives, delivers, and
forwards $\alpha_c^1$, for it improves its best partition. Then it
receives and discards $\delta_a$, for its best partition does not
match the deleted one. The bottom part of Figure~\ref{fig:problemD}
shows that eventually, $c$ stays in the deleted partition $P_a$ for
not having received $\delta_a$ that $b$ blocked earlier. As a
cascading effect, not only $c$ wrongfully believes that it belongs to
$a$'s partition when $a$ already deleted it, but it could contribute
to its inconsistency by blocking farther but up-to-date messages from
actual sources. Using local knowledge only, the system needs to purge
all stale messages to guarantee consistent partitioning.

>>>>

At any time, a source can revoke its status of source by executing a
\texttt{Del} operation, hence deleting its partition from the
system. All \processes that belong to this partition must eventually
choose another partition to belong to.

A naive implementation resembles echos in acoustics:
\underline{d}elete notifications $\delta$ propagate as long as
receivers' current partition is the targeted one, and when delete
notifications reach the bordering \processes of the deleted partition,
it triggers a competition that goes backward to fill the gap left open
by removals.  For example, in Figure~\ref{fig:del}, two partitions
initially exist: $P_a$ and $P_d$ that respectively include $\{a\}$,
and $\{b, c, d\}$. In Figure~\ref{fig:delA}, \Process~$a$ deletes its
partition. It notifies all neighboring \processes~--~here only
\Process~$b$~-- that may belong to its partition using \NAMEB. Upon
receipt, \Process~$b$ discards the delete notification $\delta_a$
since $\delta_a$ does not target the former's partition
$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
be the best for \Process~$a$. Eventually, every \process belongs to
Partition $P_d$. In this scenario, they reach consistent partitioning.

@@

\input{input/figundoproblem.tex}

@@

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It produces an echo but since $\alpha_c^3$ is already transiting
towards $a$, we simplify it. Finally, Figure~\ref{fig:problemD} shows
that eventually, $c$ stays in the deleted partition $P_a$ for not
having received $\delta_a$ that $b$ blocked earlier. As a cascading
effect, not only $c$ wrongfully believes that it belongs to $a$'s
partition when $a$ already deleted it, but it could contribute to its
inconsistency by blocking farther but up-to-date messages from actual
sources. The system needs to purge all stale messages to guarantee
consistent partitioning.
